DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-06 paper/main.tex
abstract again

\maketitle
\thispagestyle{empty}
\begin{abstract}
We present DeepPicar, a low-cost deep neural network (DNN) based
autonomous car platform. DeepPicar is a small scale
replication of a real self-driving car called Dave-2 by NVIDIA, which
drove public roads using a deep convolutional network (CNN), which
takes images from a front-facing camera as input and produces
car steering angles as output. DeepPicar uses the exact same network
architecture---9 layers, 27 million connections and 24K
parameters---and can be trained to drives itself using a small web
camera in real-time on a modest Raspberry Pi 3 quad-core computing
platform. Using DeepPicar, we analyze Pi 3's computing capabilities to 
support end-to-end deep learning based real-time control of autonomous
vehicles. We also systematically compare other contemporary embedded
computing platforms using the DeepPicar's deep learning control system
as a workload.
We find all tested platforms, including the Pi3, are capable of
supporting deep-learning based real-time control, from 20 Hz up to 100
Hz, depending on hardware platform. 
However, shared resource contention remains an
important issue that must be considered in applying deep-learning
models on shared memory based embedded computing platforms.

>>>>

\maketitle
\thispagestyle{empty}
\begin{abstract}
We present DeepPicar, a low-cost deep neural network (DNN) based
autonomous car platform. DeepPicar is a small scale
replication of a real self-driving car called Dave-2 by NVIDIA, which
drove public roads using a deep convolutional network (CNN) that
takes images from a front-facing camera as input and produces
car steering angles as output. DeepPicar uses the exact same network
architecture---9 layers, 27 million connections and 24K
parameters---and can be trained to drives itself in real-time using a
web camera and a modest Raspberry Pi 3 quad-core platform.
Using DeepPicar, we analyze Pi 3's computing capabilities to 
support end-to-end deep learning based real-time control of autonomous
vehicles. We also systematically compare other contemporary embedded
computing platforms using the DeepPicar's CNN based real-time control
software as a workload. 
We find all tested platforms, including the Pi3, are capable of
supporting deep-learning based real-time control, from 20 Hz up to 100
Hz, depending on hardware platform. 
However, shared resource contention remains an
important issue that must be considered in applying deep-learning
models on shared memory based embedded computing platforms.
